# tldtools

[![CRAN Status Badge](https://www.r-pkg.org/badges/version/tldtools)](https://cran.r-project.org/package=tldtools)
[![R-CMD-check](https://github.com/trevorld/tldtools/actions/workflows/R-CMD-check.yaml/badge.svg?branch=main)](https://github.com/trevorld/tldtools/actions)

### Table of Contents

* [Overview](#overview)
* [Installation](#installation)
* [Examples](#examples)
* [Related Links](#links)

## <a name="overview">Overview</a>

This package provides functions that help me set up my GitHub repositories and R packages the way I like them.

## <a name="installation">Installation</a>

```r
remotes::install_github("trevorld/tldtools")
```

You also need to install the [`gh` command](https://cli.github.com/) and
afterwards in a terminal run `gh auth login` to authenticate with your GitHub account or alternatively
set an appropriate `GITHUB_TOKEN` environmental variable.

## <a name="examples">Examples</a>

```{r check_github_settings}
# requires `gh` installed and authenticated and working directory in Github repository
library("tldtools")
check_github_labels()
check_github_settings()
```

```{r check_air}
library("tldtools")
check_air()
```

## <a name="links">Related Links</a>

* [`{ghcli}` R package](https://github.com/trevorld/ghcli)
* [`{usethis}` R package](https://github.com/r-lib/usethis)
